---
title: "HCAMP Symptom Cluster Data"
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    source_code: embed
    vertical_layout: scroll
    theme: united
resource_files:
- data/rtl_description.xlsx
- data/rtp_steps.xlsx
- data/cluster_scores.xlsx
- data/pcss_items.xlsx
- data/impact_data.csv
- data/four_post_injury_test_impact_sims_merge.csv
- data/three_post_injury_test_impact_sims_merge.csv
- data/two_post_injury_test_impact_sims_merge.csv
- data/one_post_injury_test_impact_sims_merge.csv
- data/four_post_injury_impact_test.csv
- data/three_post_injury_impact_test.csv
- data/two_post_injury_impact_test.csv
- data/one_post_injury_impact_test.csv
- data/sims_concussion_data.csv
---

```{r setup, include=FALSE}
library(shiny)
library(flexdashboard)
library(tidyverse)
library(here)
library(janitor)
library(rio)
library(colorblindr)
library(gghighlight)
library(forcats)
library(ggrepel)
library(knitr)
library(kableExtra)
library(reactable)
library(plotly)
library(glue)
library(fs)
library(rstatix)
library(ggpubr)
library(writexl) 
library(remotes)
library(profvis) 
library(scales)

theme_set(theme_minimal(15) +
            theme(legend.position = "bottom",
                  panel.grid.major.x = element_line(color = "gray60"),
                  panel.grid.minor.x = element_blank(),
                  panel.grid.major.y = element_blank())
          )

```

```{r global, include=FALSE}
#all clean sims data
sims_concussion_data <- read_csv(here("data", "sims_concussion_data.csv"))

sims_concussion_data <- sims_concussion_data %>% 
  mutate(age = as.factor(age))

#impact data only

one_impact_test <- read_csv(here("data", "one_post_injury_impact_test.csv"))

two_impact_test <- read_csv(here("data", "two_post_injury_impact_test.csv"))

three_impact_test <- read_csv(here("data", "three_post_injury_impact_test.csv"))

four_impact_test <- read_csv(here("data", "four_post_injury_impact_test.csv"))

# impact sims merge data

one_impact_sims <- read_csv(here("data", "one_post_injury_test_impact_sims_merge.csv"))

two_impact_sims <- read_csv(here("data", "two_post_injury_test_impact_sims_merge.csv"))

three_impact_sims <- read_csv(here("data", "three_post_injury_test_impact_sims_merge.csv"))

four_impact_sims <- read_csv(here("data", "four_post_injury_test_impact_sims_merge.csv"))

# pcss items 

pcss_items <- import(here("data", "pcss_items.xlsx"),
               setclass = "tbl_df") 

pcss_items_data <- import(here("data", "pcss_items_data.xlsx"),
               setclass = "tbl_df") 

pcss_cluster <- import(here("data", "cluster_scores.xlsx"),
               setclass = "tbl_df") 
```


# Symptom Comparisons

Sidebar {.sidebar}
------------

Symptoms that appear to be rated with higher severity more consistently: 

  1. Headache 
  2. Difficulty concentrating 
  3. Difficulty remembering 
  4. Irritability 
  5. Light sensitivity 
  
Symptoms from the headache-migraine, cognitive and anxiety-mood clusters appear to remain elevated throughout recovery. 

The vestibular cluster symptom of dizziness appears to be rated highest at the time of first testing and lessen in severity across the recovery time. 

```{r, include=FALSE}
one_impact_test_cluster <- one_impact_test %>% 
  pivot_longer(
    cols = c(32:37),
    names_to = "symptom_cluster",
    values_to = "post_injury_1_score",
    names_pattern = "(.*)_score_post_injury_1"
  ) %>% 
  select(c(1:8, 37, 38))

one_impact_test_symptoms <- one_impact_test %>% 
  pivot_longer(
    cols = c(9:30),
    names_to = "symptom",
    names_prefix = "pcss_",
    values_to = "post_injury_1_rating",
    names_pattern = "(.*)_post_injury_1"
  ) %>% 
  select(c(1:15, 21, 22))

tst_aov <- aov(total_symptom_score_post_injury_1 ~ post_injury_1_rating,
               data = one_impact_test_symptoms)

summary(tst_aov)

one_impact_test_symptoms <- left_join(one_impact_test_symptoms, pcss_items_data)

```

```{r, include=FALSE}

two_impact_test_1 <- two_impact_test %>% 
  select(passport_id, gender, contains("_post_injury_1"))

two_impact_test_2 <- two_impact_test %>% 
  select(passport_id, gender, contains("_post_injury_2"))

two_impact_test_1_symptoms <- two_impact_test_1 %>% 
  pivot_longer(
    cols = c(7:28),
    names_to = "symptom",
    names_prefix = "pcss_",
    values_to = "post_injury_1_rating",
    names_pattern = "(.*)_post_injury_1"
  ) %>% 
  select(-c(14:18))

two_impact_test_1_symptoms <- left_join(two_impact_test_1_symptoms, pcss_items_data)

two_impact_test_2_symptoms <- two_impact_test_2 %>% 
  pivot_longer(
    cols = c(7:28),
    names_to = "symptom",
    names_prefix = "pcss_",
    values_to = "post_injury_2_rating",
    names_pattern = "(.*)_post_injury_2"
  ) %>% 
  select(-c(14:18))

two_impact_test_2_symptoms <- left_join(two_impact_test_2_symptoms, pcss_items_data)

```

```{r, include=FALSE}
three_impact_test_1 <- three_impact_test %>% 
  select(passport_id, gender, contains("_post_injury_1"))

three_impact_test_2 <- three_impact_test %>% 
  select(passport_id, gender, contains("_post_injury_2"))

three_impact_test_3 <- three_impact_test %>% 
  select(passport_id, gender, contains("_post_injury_3"))

three_impact_test_1_symptoms <- three_impact_test_1 %>% 
  pivot_longer(
    cols = c(7:28),
    names_to = "symptom",
    names_prefix = "pcss_",
    values_to = "post_injury_1_rating",
    names_pattern = "(.*)_post_injury_1"
  ) %>% 
  select(-c(14:18))

three_impact_test_1_symptoms <- left_join(three_impact_test_1_symptoms, pcss_items_data)


three_impact_test_2_symptoms <- three_impact_test_2 %>% 
  pivot_longer(
    cols = c(7:28),
    names_to = "symptom",
    names_prefix = "pcss_",
    values_to = "post_injury_2_rating",
    names_pattern = "(.*)_post_injury_2"
  ) %>% 
  select(-c(14:18))

three_impact_test_2_symptoms <- left_join(three_impact_test_2_symptoms, pcss_items_data)

three_impact_test_3_symptoms <- three_impact_test_3 %>% 
  pivot_longer(
    cols = c(7:28),
    names_to = "symptom",
    names_prefix = "pcss_",
    values_to = "post_injury_3_rating",
    names_pattern = "(.*)_post_injury_3"
  ) %>% 
  select(-c(14:18))

three_impact_test_3_symptoms <- left_join(three_impact_test_3_symptoms, pcss_items_data)

```

```{r, include=FALSE}
four_impact_test_1 <- four_impact_test %>% 
  select(passport_id, gender, contains("_post_injury_1"))

four_impact_test_2 <- four_impact_test %>% 
  select(passport_id, gender, contains("_post_injury_2"))

four_impact_test_3 <- four_impact_test %>% 
  select(passport_id, gender, contains("_post_injury_3"))

four_impact_test_4 <- four_impact_test %>% 
  select(passport_id, gender, contains("_post_injury_4"))

four_impact_test_1_symptoms <- four_impact_test_1 %>% 
  pivot_longer(
    cols = c(7:28),
    names_to = "symptom",
    names_prefix = "pcss_",
    values_to = "post_injury_1_rating",
    names_pattern = "(.*)_post_injury_1"
  ) %>% 
  select(-c(14:18))

four_impact_test_1_symptoms <- left_join(four_impact_test_1_symptoms, pcss_items_data)


four_impact_test_2_symptoms <- four_impact_test_2 %>% 
  pivot_longer(
    cols = c(7:28),
    names_to = "symptom",
    names_prefix = "pcss_",
    values_to = "post_injury_2_rating",
    names_pattern = "(.*)_post_injury_2"
  ) %>% 
  select(-c(14:18))

four_impact_test_2_symptoms <- left_join(four_impact_test_2_symptoms, pcss_items_data)

four_impact_test_3_symptoms <- four_impact_test_3 %>% 
  pivot_longer(
    cols = c(7:28),
    names_to = "symptom",
    names_prefix = "pcss_",
    values_to = "post_injury_3_rating",
    names_pattern = "(.*)_post_injury_3"
  ) %>% 
  select(-c(14:18))

four_impact_test_3_symptoms <- left_join(four_impact_test_3_symptoms, pcss_items_data)


four_impact_test_4_symptoms <- four_impact_test_4 %>% 
  pivot_longer(
    cols = c(7:28),
    names_to = "symptom",
    names_prefix = "pcss_",
    values_to = "post_injury_4_rating",
    names_pattern = "(.*)_post_injury_4"
  ) %>% 
  select(-c(14:18))

four_impact_test_4_symptoms <- left_join(four_impact_test_4_symptoms, pcss_items_data)
```


Row {.tabset}
-----------------------------------------------------------------------

### One Test 

```{r, include=FALSE}
all_symptom_tbl <- one_impact_test_symptoms %>% 
    group_by(gender, cluster, symptom) %>% 
    summarize(Mean = mean(post_injury_1_rating),
              SD = sd(post_injury_1_rating),
              Min = min(post_injury_1_rating),
              Max = max(post_injury_1_rating),
              Total = length(post_injury_1_rating)) %>% 
    mutate(Mean = as.numeric(Mean),
           SD = as.numeric(SD),
           Min = as.numeric(Min),
           Max = as.numeric(Max)) %>% 
    arrange(desc(Mean)) %>% 
    mutate_if(is.numeric, round, 2) %>% 
    reactable(
      defaultColDef = colDef(align = "center"),
      columns = list(
        gender = colDef(name = "Gender"),
        cluster = colDef(name = "Symptom Cluster"),
        symptom = colDef(name = "Symptom"),
        Mean = colDef(format = colFormat(separators = TRUE)),
        SD = colDef(format = colFormat(separators = TRUE)),
        Min = colDef(format = colFormat(separators = TRUE)),
        Max = colDef(format = colFormat(separators = TRUE)),
        Total = colDef(format = colFormat(separators = TRUE, suffix = " concussions"))
      ),
      pagination = TRUE,
      striped = TRUE,
      outlined = TRUE,
      compact = TRUE,
      highlight = TRUE,
      bordered = TRUE,
      searchable = TRUE
    )

symptom_tbl <- function(df, a, b, c, d) {
    df %>% 
    group_by({{a}}, {{b}}, {{c}}) %>% 
    summarize(Mean = mean({{d}}),
              SD = sd({{d}}),
              Min = min({{d}}),
              Max = max({{d}}),
              Total = length({{d}})) %>% 
    mutate(Mean = as.numeric(Mean),
           SD = as.numeric(SD),
           Min = as.numeric(Min),
           Max = as.numeric(Max)) %>% 
    arrange(desc(Mean)) %>% 
    mutate_if(is.numeric, round, 2) %>% 
    reactable(
      defaultColDef = colDef(align = "center"),
      columns = list(
        gender = colDef(name = "Gender"),
        cluster = colDef(name = "Symptom Cluster"),
        symptom = colDef(name = "Symptom"),
        Mean = colDef(format = colFormat(separators = TRUE)),
        SD = colDef(format = colFormat(separators = TRUE)),
        Min = colDef(format = colFormat(separators = TRUE)),
        Max = colDef(format = colFormat(separators = TRUE)),
        Total = colDef(format = colFormat(separators = TRUE, suffix = " concussions"))
      ),
      pagination = TRUE,
      striped = TRUE,
      outlined = TRUE,
      compact = TRUE,
      highlight = TRUE,
      bordered = TRUE,
      searchable = TRUE
    )
}

symptom_tbl_over_three <- function(df, a, b, c, d) {
    df %>% 
    group_by({{a}}, {{b}}, {{c}}) %>% 
    filter({{d}} >=3) %>% 
    summarize(Mean = mean({{d}}),
              SD = sd({{d}}),
              Min = min({{d}}),
              Max = max({{d}}),
              Total = length({{d}})) %>% 
    mutate(Mean = as.numeric(Mean),
           SD = as.numeric(SD),
           Min = as.numeric(Min),
           Max = as.numeric(Max)) %>% 
    arrange(desc(Mean)) %>% 
    mutate_if(is.numeric, round, 2) %>% 
    reactable(
      defaultColDef = colDef(align = "center"),
      columns = list(
        gender = colDef(name = "Gender"),
        cluster = colDef(name = "Symptom Cluster"),
        symptom = colDef(name = "Symptom"),
        Mean = colDef(format = colFormat(separators = TRUE)),
        SD = colDef(format = colFormat(separators = TRUE)),
        Min = colDef(format = colFormat(separators = TRUE)),
        Max = colDef(format = colFormat(separators = TRUE)),
        Total = colDef(format = colFormat(separators = TRUE, suffix = " concussions"))
      ),
      pagination = TRUE,
      striped = TRUE,
      outlined = TRUE,
      compact = TRUE,
      highlight = TRUE,
      bordered = TRUE,
      searchable = TRUE
    )
}

```


```{r, include=TRUE}
symptom_tbl(one_impact_test_symptoms, gender, cluster, symptom, post_injury_1_rating)
```


Row {.tabset}
-----------------------------------------------------------------------

### Two Tests - Test 1

```{r, include=TRUE}
symptom_tbl(two_impact_test_1_symptoms, gender, cluster, symptom, post_injury_1_rating)
```

### Two Tests - Test 2 

```{r, include=TRUE}
symptom_tbl(two_impact_test_2_symptoms, gender, cluster, symptom, post_injury_2_rating)
```


Row {.tabset}
-----------------------------------------------------------------------

### Three Tests - Test 1

```{r, include=TRUE}
symptom_tbl(three_impact_test_1_symptoms, gender, cluster, symptom, post_injury_1_rating)
```

### Three Tests - Test 2 

```{r, include=TRUE}
symptom_tbl(three_impact_test_2_symptoms, gender, cluster, symptom, post_injury_2_rating)
```

### Three Tests - Test 3 

```{r, include=TRUE}
symptom_tbl(three_impact_test_3_symptoms, gender, cluster, symptom, post_injury_3_rating)
```



Row {.tabset}
-----------------------------------------------------------------------

### Four Tests - Test 1

```{r, include=TRUE}
symptom_tbl(four_impact_test_1_symptoms, gender, cluster, symptom, post_injury_1_rating)
```

### Four Tests - Test 2 

```{r, include=TRUE}
symptom_tbl(four_impact_test_2_symptoms, gender, cluster, symptom, post_injury_2_rating)
```

### Four Tests - Test 3

```{r, include=TRUE}
symptom_tbl(four_impact_test_3_symptoms, gender, cluster, symptom, post_injury_3_rating)
```

### Four Tests - Test 4

```{r, include=TRUE}
symptom_tbl(four_impact_test_4_symptoms, gender, cluster, symptom, post_injury_4_rating)
```

# Cluster Comparisons 

Sidebar {.sidebar}
------------

Symptom Cluster Potential Symptom Severity Range:

  1. Headache-Migraine Cluster: 0 - 18 (3 symptoms)
  2. Cognitive Cluster: 0 - 24 (4 symptoms)
  3. Anxiety-Mood Cluster: 0 - 30 (5 symptoms)
  4. Ocular-Motor Cluster: 0 - 6 (1 symptom)
  5. Vestibular Cluster: 0 - 24 (4 symptoms)
  6. Sleep Cluster: 0 - 30 (5 symptoms)
  
  
  Row {.tabset}
-----------------------------------------------------------------------

### 1 Test Cluster Summary 

```{r, include=FALSE}
clusters_one_impact_test <- one_impact_test %>% 
  select(c(1:8, 32:37)) %>% 
  mutate(X1 = as.character(X1),
         row = as.character(row),
         age = as.character(age))

str(clusters_one_impact_test)

# normalize <- function(x) {
# return ((x - min(x)) / (max(x) - min(x)))
# }

rescale01b <- function(x) {
  if(is.numeric(x)) {
    z <- na.omit(x)
    min_z <- min(z)
    max_z <- max(z)
    (z - min_z) / (max_z - min_z)
  }
  else {
    return()
  }
}

rescale01b(c(0, 5, 10))

clusters_one_impact_test_scaled <- map_df(clusters_one_impact_test, rescale01b)

clusters_one_impact_test_scaled <- bind_cols(clusters_one_impact_test, 
                                             clusters_one_impact_test_scaled)

clusters_one_impact_test_scaled <- clusters_one_impact_test_scaled %>% 
  select(-c(9:14))

clusters_one_impact_test_scaled_long <- clusters_one_impact_test_scaled %>% 
    pivot_longer(
    cols = c(9:14),
    names_to = "symptom_cluster",
    values_to = "post_injury_1_score",
    names_pattern = "(.*)_score_post_injury_1"
  ) 

```

```{r, include=FALSE}
#summary 
cluster_smry_tbl <- function(df, x) {
  df %>% 
  group_by(symptom_cluster) %>% 
  summarize(mean = mean({{x}}),
            sd = sd({{x}}),
            min = min({{x}}),
            max = max({{x}}),
            total = length({{x}})) %>%
  mutate(mean = as.numeric(mean),
         sd = as.numeric(sd),
         min = as.numeric(min),
         max = as.numeric(max),
         total = as.numeric(total)) %>% 
  reactable(
    columns = list(
      symptom_cluster = colDef(name = "Symptom Cluster",
                            align = "center"),
      mean = colDef(name = "Mean",
                    align = "center",
                    format = colFormat(digits = 2, separators = TRUE)),
      sd = colDef(name = "SD",
                  align = "center",
                  format = colFormat(digits = 2, separators = TRUE)),
      min = colDef(name = "Min",
                   align = "center",
                   format = colFormat(separators = TRUE)),
      max = colDef(name = "Max",
                   align = "center",
                   format = colFormat(separators = TRUE)),
      total = colDef(name = "Total",
                     align = "center",
                   format = colFormat(separators = TRUE, suffix = " concussions"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE
  )
}

cluster_smry_tbl(clusters_one_impact_test_scaled_long, post_injury_1_score)
```

```{r, include=TRUE}
cluster_smry_tbl(clusters_one_impact_test_scaled_long, post_injury_1_score)
```

### 1 Test Cluster Boxplot 

```{r, include=FALSE}
cluster_bxp_1 <- ggplot(clusters_one_impact_test_scaled_long,
                      aes(symptom_cluster, post_injury_1_score)) +
  geom_boxplot() + 
  labs(x = "Symptom Cluster",
       y = "Scaled Severity Score") +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 25))

cluster_bxp <- function(df, x, y) {
  ggplot(df, aes({{x}}, {{y}})) +
  geom_boxplot() + 
  labs(x = "Symptom Cluster",
       y = "Scaled Severity Score") +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 25))
}

cluster_bxp(clusters_one_impact_test_scaled_long, symptom_cluster, post_injury_1_score)

```

```{r, include=TRUE}
ggplotly(cluster_bxp(clusters_one_impact_test_scaled_long, symptom_cluster, post_injury_1_score))
```

### 1 Test Cluster ANOVA 

```{r, include=FALSE}
cluster_one_test_aov <- aov(post_injury_1_score ~ symptom_cluster, 
                            data = clusters_one_impact_test_scaled_long)

summary(cluster_one_test_aov)

cluster_one_test_aov
```

```{r, include=TRUE}
summary(cluster_one_test_aov)
```

### 1 Test Cluster PWC

```{r, include=FALSE}
cluster_one_test_aov_pwc <- clusters_one_impact_test_scaled_long %>% 
  pairwise_t_test(
    post_injury_1_score ~ symptom_cluster, paired = FALSE,
    p.adjust.method = "bonferroni"
  )

cluster_one_test_aov_pwc <- cluster_one_test_aov_pwc %>% 
  mutate_at(vars(p, p.adj), list(~ round(., 2)))
```

```{r, include=TRUE}
cluster_one_test_aov_pwc %>% 
  reactable()
```


Row {.tabset}
-----------------------------------------------------------------------

### 2 Tests Cluster Summary - Test 1

```{r, include=FALSE}

clusters_two_impact_test_1 <- two_impact_test %>% 
  select(c(1:12, contains("_post_injury_1"))) %>% 
    mutate(X1 = as.character(X1),
         row = as.character(row),
         age_post_injury_1 = as.character(age_post_injury_1),
         age_post_injury_2 = as.character(age_post_injury_2))

clusters_two_impact_test_1 <- clusters_two_impact_test_1 %>% 
  select(c(1:12, 36:41))

clusters_two_impact_test_1_scaled <- map_df(clusters_two_impact_test_1, rescale01b)

clusters_two_impact_test_1_scaled <- bind_cols(clusters_two_impact_test_1, 
                                             clusters_two_impact_test_1_scaled)

clusters_two_impact_test_1_scaled <- clusters_two_impact_test_1_scaled %>% 
  select(-c(13:18))

clusters_two_impact_test_1_long <- clusters_two_impact_test_1_scaled %>% 
    pivot_longer(
    cols = c(13:18),
    names_to = "symptom_cluster",
    values_to = "post_injury_1_score",
    names_pattern = "(.*)_score_post_injury_1"
  ) 


clusters_two_impact_test_2 <- two_impact_test %>% 
  select(c(1:12, contains("_post_injury_2"))) %>% 
    mutate(X1 = as.character(X1),
         row = as.character(row),
         age_post_injury_1 = as.character(age_post_injury_1),
         age_post_injury_2 = as.character(age_post_injury_2))

clusters_two_impact_test_2 <- clusters_two_impact_test_2 %>% 
  select(c(1:12, 36:41))

clusters_two_impact_test_2_scaled <- map_df(clusters_two_impact_test_2, rescale01b)

clusters_two_impact_test_2_scaled <- bind_cols(clusters_two_impact_test_2, 
                                             clusters_two_impact_test_2_scaled)

clusters_two_impact_test_2_scaled <- clusters_two_impact_test_2_scaled %>% 
  select(-c(13:18))

clusters_two_impact_test_2_long <- clusters_two_impact_test_2_scaled %>% 
    pivot_longer(
    cols = c(13:18),
    names_to = "symptom_cluster",
    values_to = "post_injury_2_score",
    names_pattern = "(.*)_score_post_injury_2"
  ) 

clusters_two_impact_test_complete <- left_join(clusters_two_impact_test_1_long,
                                               clusters_two_impact_test_2_long)
```

```{r, include=TRUE}
cluster_smry_tbl(clusters_two_impact_test_complete, post_injury_1_score)
```

### 2 Tests Cluster Boxplot - Test 1

```{r, include=TRUE}
ggplotly(cluster_bxp(clusters_two_impact_test_complete, 
                     symptom_cluster, post_injury_1_score))
```

### 2 Tests Cluster ANOVA - Test 1

```{r, include=FALSE}
cluster_two_tests_aov_1 <- aov(post_injury_1_score ~ symptom_cluster, 
                            data = clusters_two_impact_test_complete)
```

```{r, include=TRUE}
summary(cluster_two_tests_aov_1)
```

### 2 Tests Cluster PWC - Test 1

```{r, include=FALSE}
cluster_two_tests_aov_pwc_1 <- clusters_two_impact_test_complete %>% 
  pairwise_t_test(
    post_injury_1_score ~ symptom_cluster, paired = FALSE,
    p.adjust.method = "bonferroni"
  )

cluster_two_tests_aov_pwc_1 <- cluster_two_tests_aov_pwc_1 %>% 
  mutate_at(vars(p, p.adj), list(~ round(., 2)))
```

```{r, include=TRUE}
cluster_two_tests_aov_pwc_1 %>% 
  reactable()
```


### 2 Tests Cluster Summary - Test 2

```{r, include=TRUE}
cluster_smry_tbl(clusters_two_impact_test_complete, post_injury_2_score)
```

### 2 Tests Cluster Boxplot - Test 2

```{r, include=TRUE}
ggplotly(cluster_bxp(clusters_two_impact_test_complete, 
                     symptom_cluster, post_injury_2_score))
```

### 2 Tests Cluster ANOVA - Test 2

```{r, include=FALSE}
cluster_two_tests_aov_2 <- aov(post_injury_2_score ~ symptom_cluster, 
                            data = clusters_two_impact_test_complete)
```

```{r, include=TRUE}
summary(cluster_two_tests_aov_2)
```

### 2 Tests Cluster PWC - Test 2

```{r, include=FALSE}
cluster_two_tests_aov_pwc_2 <- clusters_two_impact_test_complete %>% 
  pairwise_t_test(
    post_injury_2_score ~ symptom_cluster, paired = FALSE,
    p.adjust.method = "bonferroni"
  )

cluster_two_tests_aov_pwc_2 <- cluster_two_tests_aov_pwc_2 %>% 
  mutate_at(vars(p, p.adj), list(~ round(., 2)))
```

```{r, include=TRUE}
cluster_two_tests_aov_pwc_2 %>% 
  reactable()
```



Row {.tabset}
-----------------------------------------------------------------------

### 3 Tests Cluster Summary - Test 1

```{r, include=FALSE}

clusters_three_impact_test_1 <- three_impact_test %>% 
  select(c(1:16, contains("_post_injury_1"))) %>% 
    mutate(X1 = as.character(X1),
         row = as.character(row),
         age_post_injury_1 = as.character(age_post_injury_1),
         age_post_injury_2 = as.character(age_post_injury_2),
         age_post_injury_3 = as.character(age_post_injury_3))

clusters_three_impact_test_1 <- clusters_three_impact_test_1 %>% 
  select(c(1:16, 40:45))

clusters_three_impact_test_1_scaled <- map_df(clusters_three_impact_test_1, rescale01b)

clusters_three_impact_test_1_scaled <- bind_cols(clusters_three_impact_test_1, 
                                             clusters_three_impact_test_1_scaled)

clusters_three_impact_test_1_scaled <- clusters_three_impact_test_1_scaled %>% 
  select(-c(17:22))

clusters_three_impact_test_1_long <- clusters_three_impact_test_1_scaled %>% 
    pivot_longer(
    cols = c(17:22),
    names_to = "symptom_cluster",
    values_to = "post_injury_1_score",
    names_pattern = "(.*)_score_post_injury_1"
  ) 


clusters_three_impact_test_2 <- three_impact_test %>% 
  select(c(1:16, contains("_post_injury_2"))) %>% 
    mutate(X1 = as.character(X1),
         row = as.character(row),
         age_post_injury_1 = as.character(age_post_injury_1),
         age_post_injury_2 = as.character(age_post_injury_2),
         age_post_injury_3 = as.character(age_post_injury_3))

clusters_three_impact_test_2 <- clusters_three_impact_test_2 %>% 
  select(c(1:16, 40:45))

clusters_three_impact_test_2_scaled <- map_df(clusters_three_impact_test_2, rescale01b)

clusters_three_impact_test_2_scaled <- bind_cols(clusters_three_impact_test_2, 
                                             clusters_three_impact_test_2_scaled)

clusters_three_impact_test_2_scaled <- clusters_three_impact_test_2_scaled %>% 
  select(-c(17:22))

clusters_three_impact_test_2_long <- clusters_three_impact_test_2_scaled %>% 
    pivot_longer(
    cols = c(17:22),
    names_to = "symptom_cluster",
    values_to = "post_injury_2_score",
    names_pattern = "(.*)_score_post_injury_2"
  ) 


clusters_three_impact_test_3 <- three_impact_test %>% 
  select(c(1:16, contains("_post_injury_3"))) %>% 
    mutate(X1 = as.character(X1),
         row = as.character(row),
         age_post_injury_1 = as.character(age_post_injury_1),
         age_post_injury_2 = as.character(age_post_injury_2),
         age_post_injury_3 = as.character(age_post_injury_3))

clusters_three_impact_test_3 <- clusters_three_impact_test_3 %>% 
  select(c(1:16, 40:45))

clusters_three_impact_test_3_scaled <- map_df(clusters_three_impact_test_3, rescale01b)

clusters_three_impact_test_3_scaled <- bind_cols(clusters_three_impact_test_3, 
                                             clusters_three_impact_test_3_scaled)

clusters_three_impact_test_3_scaled <- clusters_three_impact_test_3_scaled %>% 
  select(-c(17:22))

clusters_three_impact_test_3_long <- clusters_three_impact_test_3_scaled %>% 
    pivot_longer(
    cols = c(17:22),
    names_to = "symptom_cluster",
    values_to = "post_injury_3_score",
    names_pattern = "(.*)_score_post_injury_3"
  ) 

clusters_three_impact_test_join_1 <- left_join(clusters_three_impact_test_1_long,
                                               clusters_three_impact_test_2_long)

clusters_three_impact_test_complete <- left_join(clusters_three_impact_test_join_1, 
                                                 clusters_three_impact_test_3_long)
```


```{r, include=TRUE}
cluster_smry_tbl(clusters_three_impact_test_complete, post_injury_1_score)
```

### 3 Tests Cluster Boxplot - Test 1

```{r, include=TRUE}
ggplotly(cluster_bxp(clusters_three_impact_test_complete, 
                     symptom_cluster, post_injury_1_score))
```

### 3 Tests Cluster ANOVA - Test 1

```{r, include=FALSE}
cluster_three_tests_aov_1 <- aov(post_injury_1_score ~ symptom_cluster, 
                            data = clusters_three_impact_test_complete)
```

```{r, include=TRUE}
summary(cluster_three_tests_aov_1)
```

### 3 Tests Cluster PWC - Test 1

```{r, include=FALSE}
cluster_three_tests_aov_pwc_1 <- clusters_three_impact_test_complete %>% 
  pairwise_t_test(
    post_injury_1_score ~ symptom_cluster, paired = FALSE,
    p.adjust.method = "bonferroni"
  )

cluster_three_tests_aov_pwc_1 <- cluster_three_tests_aov_pwc_1 %>% 
  mutate_at(vars(p, p.adj), list(~ round(., 2)))
```

```{r, include=TRUE}
cluster_three_tests_aov_pwc_1 %>% 
  reactable()
```


### 3 Tests Cluster Summary - Test 2

```{r, include=TRUE}
cluster_smry_tbl(clusters_three_impact_test_complete, post_injury_2_score)
```

### 3 Tests Cluster Boxplot - Test 2

```{r, include=TRUE}
ggplotly(cluster_bxp(clusters_three_impact_test_complete, 
                     symptom_cluster, post_injury_2_score))
```

### 3 Tests Cluster ANOVA - Test 2

```{r, include=FALSE}
cluster_three_tests_aov_2 <- aov(post_injury_2_score ~ symptom_cluster, 
                            data = clusters_three_impact_test_complete)
```

```{r, include=TRUE}
summary(cluster_three_tests_aov_2)
```

### 3 Tests Cluster PWC - Test 2

```{r, include=FALSE}
cluster_three_tests_aov_pwc_2 <- clusters_three_impact_test_complete %>% 
  pairwise_t_test(
    post_injury_2_score ~ symptom_cluster, paired = FALSE,
    p.adjust.method = "bonferroni"
  )

cluster_three_tests_aov_pwc_2 <- cluster_three_tests_aov_pwc_2 %>% 
  mutate_at(vars(p, p.adj), list(~ round(., 2)))
```

```{r, include=TRUE}
cluster_three_tests_aov_pwc_2 %>% 
  reactable()
```


### 3 Tests Cluster Summary - Test 3

```{r, include=TRUE}
cluster_smry_tbl(clusters_three_impact_test_complete, post_injury_3_score)
```

### 3 Tests Cluster Boxplot - Test 3

```{r, include=TRUE}
ggplotly(cluster_bxp(clusters_three_impact_test_complete, 
                     symptom_cluster, post_injury_3_score))
```

### 3 Tests Cluster ANOVA - Test 3

```{r, include=FALSE}
cluster_three_tests_aov_3 <- aov(post_injury_3_score ~ symptom_cluster, 
                            data = clusters_three_impact_test_complete)
```

```{r, include=TRUE}
summary(cluster_three_tests_aov_3)
```

### 3 Tests Cluster PWC - Test 3

```{r, include=FALSE}
cluster_three_tests_aov_pwc_3 <- clusters_three_impact_test_complete %>% 
  pairwise_t_test(
    post_injury_3_score ~ symptom_cluster, paired = FALSE,
    p.adjust.method = "bonferroni"
  )

cluster_three_tests_aov_pwc_3 <- cluster_three_tests_aov_pwc_3 %>% 
  mutate_at(vars(p, p.adj), list(~ round(., 2)))
```

```{r, include=TRUE}
cluster_three_tests_aov_pwc_3 %>% 
  reactable()
```


Row {.tabset}
-----------------------------------------------------------------------

### 4 Tests Cluster Summary - Test 1

```{r, include=FALSE}

clusters_four_impact_test_1 <- four_impact_test %>% 
  select(c(1:20, contains("_post_injury_1"))) %>% 
    mutate(X1 = as.character(X1),
         row = as.character(row),
         age_post_injury_1 = as.character(age_post_injury_1),
         age_post_injury_2 = as.character(age_post_injury_2),
         age_post_injury_3 = as.character(age_post_injury_3),
         age_post_injury_4 = as.character(age_post_injury_4))

clusters_four_impact_test_1 <- clusters_four_impact_test_1 %>% 
  select(c(1:20, 44:49))

clusters_four_impact_test_1_scaled <- map_df(clusters_four_impact_test_1, rescale01b)

clusters_four_impact_test_1_scaled <- bind_cols(clusters_four_impact_test_1, 
                                             clusters_four_impact_test_1_scaled)

clusters_four_impact_test_1_scaled <- clusters_four_impact_test_1_scaled %>% 
  select(-c(21:26))

clusters_four_impact_test_1_long <- clusters_four_impact_test_1_scaled %>% 
    pivot_longer(
    cols = c(21:26),
    names_to = "symptom_cluster",
    values_to = "post_injury_1_score",
    names_pattern = "(.*)_score_post_injury_1"
  ) 

clusters_four_impact_test_2 <- four_impact_test %>% 
  select(c(1:20, contains("_post_injury_2"))) %>% 
    mutate(X1 = as.character(X1),
         row = as.character(row),
         age_post_injury_1 = as.character(age_post_injury_1),
         age_post_injury_2 = as.character(age_post_injury_2),
         age_post_injury_3 = as.character(age_post_injury_3),
         age_post_injury_4 = as.character(age_post_injury_4))

clusters_four_impact_test_2 <- clusters_four_impact_test_2 %>% 
  select(c(1:20, 44:49))

clusters_four_impact_test_2_scaled <- map_df(clusters_four_impact_test_2, rescale01b)

clusters_four_impact_test_2_scaled <- bind_cols(clusters_four_impact_test_2, 
                                             clusters_four_impact_test_2_scaled)

clusters_four_impact_test_2_scaled <- clusters_four_impact_test_2_scaled %>% 
  select(-c(21:26))

clusters_four_impact_test_2_long <- clusters_four_impact_test_2_scaled %>% 
    pivot_longer(
    cols = c(21:26),
    names_to = "symptom_cluster",
    values_to = "post_injury_2_score",
    names_pattern = "(.*)_score_post_injury_2"
  ) 

clusters_four_impact_test_3 <- four_impact_test %>% 
  select(c(1:20, contains("_post_injury_3"))) %>% 
    mutate(X1 = as.character(X1),
         row = as.character(row),
         age_post_injury_1 = as.character(age_post_injury_1),
         age_post_injury_2 = as.character(age_post_injury_2),
         age_post_injury_3 = as.character(age_post_injury_3),
         age_post_injury_4 = as.character(age_post_injury_4))

clusters_four_impact_test_3 <- clusters_four_impact_test_3 %>% 
  select(c(1:20, 44:49))

clusters_four_impact_test_3_scaled <- map_df(clusters_four_impact_test_3, rescale01b)

clusters_four_impact_test_3_scaled <- bind_cols(clusters_four_impact_test_3, 
                                             clusters_four_impact_test_3_scaled)

clusters_four_impact_test_3_scaled <- clusters_four_impact_test_3_scaled %>% 
  select(-c(21:26))

clusters_four_impact_test_3_long <- clusters_four_impact_test_3_scaled %>% 
    pivot_longer(
    cols = c(21:26),
    names_to = "symptom_cluster",
    values_to = "post_injury_3_score",
    names_pattern = "(.*)_score_post_injury_3"
  ) 


clusters_four_impact_test_4 <- four_impact_test %>% 
  select(c(1:20, contains("_post_injury_4"))) %>% 
    mutate(X1 = as.character(X1),
         row = as.character(row),
         age_post_injury_1 = as.character(age_post_injury_1),
         age_post_injury_2 = as.character(age_post_injury_2),
         age_post_injury_3 = as.character(age_post_injury_3),
         age_post_injury_4 = as.character(age_post_injury_4))

clusters_four_impact_test_4 <- clusters_four_impact_test_4 %>% 
  select(c(1:20, 44:49))

clusters_four_impact_test_4_scaled <- map_df(clusters_four_impact_test_4, rescale01b)

clusters_four_impact_test_4_scaled <- bind_cols(clusters_four_impact_test_4, 
                                             clusters_four_impact_test_4_scaled)

clusters_four_impact_test_4_scaled <- clusters_four_impact_test_4_scaled %>% 
  select(-c(21:26))

clusters_four_impact_test_4_long <- clusters_four_impact_test_4_scaled %>% 
    pivot_longer(
    cols = c(21:26),
    names_to = "symptom_cluster",
    values_to = "post_injury_4_score",
    names_pattern = "(.*)_score_post_injury_4"
  ) 


clusters_four_impact_test_join_1 <- left_join(clusters_four_impact_test_1_long,
                                               clusters_four_impact_test_2_long)

clusters_four_impact_test_join_2 <- left_join(clusters_four_impact_test_join_1, 
                                                 clusters_four_impact_test_3_long)

clusters_four_impact_test_complete <- left_join(clusters_four_impact_test_join_2,
                                                clusters_four_impact_test_4_long)
```


```{r, include=TRUE}
cluster_smry_tbl(clusters_four_impact_test_complete, post_injury_1_score)
```

### 4 Tests Cluster Boxplot - Test 1

```{r, include=TRUE}
ggplotly(cluster_bxp(clusters_four_impact_test_complete, 
                     symptom_cluster, post_injury_1_score))
```

### 4 Tests Cluster ANOVA - Test 1

```{r, include=FALSE}
cluster_four_tests_aov_1 <- aov(post_injury_1_score ~ symptom_cluster, 
                            data = clusters_four_impact_test_complete)
```

```{r, include=TRUE}
summary(cluster_four_tests_aov_1)
```

### 4 Tests Cluster PWC - Test 1

```{r, include=FALSE}
cluster_four_tests_aov_pwc_1 <- clusters_four_impact_test_complete %>% 
  pairwise_t_test(
    post_injury_1_score ~ symptom_cluster, paired = FALSE,
    p.adjust.method = "bonferroni"
  )

cluster_four_tests_aov_pwc_1 <- cluster_four_tests_aov_pwc_1 %>% 
  mutate_at(vars(p, p.adj), list(~ round(., 2)))
```

```{r, include=TRUE}
cluster_four_tests_aov_pwc_1 %>% 
  reactable()
```


### 4 Tests Cluster Summary - Test 2

```{r, include=TRUE}
cluster_smry_tbl(clusters_four_impact_test_complete, post_injury_2_score)
```

### 4 Tests Cluster Boxplot - Test 2

```{r, include=TRUE}
ggplotly(cluster_bxp(clusters_four_impact_test_complete, 
                     symptom_cluster, post_injury_2_score))
```

### 4 Tests Cluster ANOVA - Test 2

```{r, include=FALSE}
cluster_four_tests_aov_2 <- aov(post_injury_2_score ~ symptom_cluster, 
                            data = clusters_four_impact_test_complete)
```

```{r, include=TRUE}
summary(cluster_four_tests_aov_2)
```

### 4 Tests Cluster PWC - Test 2

```{r, include=FALSE}
cluster_four_tests_aov_pwc_2 <- clusters_four_impact_test_complete %>% 
  pairwise_t_test(
    post_injury_2_score ~ symptom_cluster, paired = FALSE,
    p.adjust.method = "bonferroni"
  )

cluster_four_tests_aov_pwc_2 <- cluster_four_tests_aov_pwc_2 %>% 
  mutate_at(vars(p, p.adj), list(~ round(., 2)))
```

```{r, include=TRUE}
cluster_four_tests_aov_pwc_2 %>% 
  reactable()
```


### 4 Tests Cluster Summary - Test 3

```{r, include=TRUE}
cluster_smry_tbl(clusters_four_impact_test_complete, post_injury_3_score)
```

### 4 Tests Cluster Boxplot - Test 3

```{r, include=TRUE}
ggplotly(cluster_bxp(clusters_four_impact_test_complete, 
                     symptom_cluster, post_injury_3_score))
```

### 4 Tests Cluster ANOVA - Test 3

```{r, include=FALSE}
cluster_four_tests_aov_3 <- aov(post_injury_3_score ~ symptom_cluster, 
                            data = clusters_four_impact_test_complete)
```

```{r, include=TRUE}
summary(cluster_four_tests_aov_3)
```

### 4 Tests Cluster PWC - Test 3

```{r, include=FALSE}
cluster_four_tests_aov_pwc_3 <- clusters_four_impact_test_complete %>% 
  pairwise_t_test(
    post_injury_3_score ~ symptom_cluster, paired = FALSE,
    p.adjust.method = "bonferroni"
  )

cluster_four_tests_aov_pwc_3 <- cluster_four_tests_aov_pwc_3 %>% 
  mutate_at(vars(p, p.adj), list(~ round(., 2)))
```

```{r, include=TRUE}
cluster_four_tests_aov_pwc_3 %>% 
  reactable()
```


### 4 Tests Cluster Summary - Test 4

```{r, include=TRUE}
cluster_smry_tbl(clusters_four_impact_test_complete, post_injury_4_score)
```

### 4 Tests Cluster Boxplot - Test 4

```{r, include=TRUE}
ggplotly(cluster_bxp(clusters_four_impact_test_complete, 
                     symptom_cluster, post_injury_4_score))
```

### 4 Tests Cluster ANOVA - Test 4

```{r, include=FALSE}
cluster_four_tests_aov_4 <- aov(post_injury_4_score ~ symptom_cluster, 
                            data = clusters_four_impact_test_complete)
```

```{r, include=TRUE}
summary(cluster_four_tests_aov_4)
```

### 4 Tests Cluster PWC - Test 4

```{r, include=FALSE}
cluster_four_tests_aov_pwc_4 <- clusters_four_impact_test_complete %>% 
  pairwise_t_test(
    post_injury_4_score ~ symptom_cluster, paired = FALSE,
    p.adjust.method = "bonferroni"
  )

cluster_four_tests_aov_pwc_4 <- cluster_four_tests_aov_pwc_4 %>% 
  mutate_at(vars(p, p.adj), list(~ round(., 2)))
```

```{r, include=TRUE}
cluster_four_tests_aov_pwc_4 %>% 
  reactable()
```
